Bow shocks, bow waves, and dust waves

### 2018-07-04 papers/Papers1234/sec-dust-bow-intro.tex
Make start on description of when dust wave crosses mhd bow shock

>>>>

The assumptions behind these models break down when the grain
trajectory intersects the outer shock of the dust-free wind-supported
bow shock.  The increased gas density in the bow shock shell will
reduce \(\Xi\), which is likely to cause recoupling in the case of
drag-confined dust waves (see also discussion in the final paragraph
of \S~\ref{sec:exist-cond-separ}).  However, detailed modeling of this
requires magnetohydrodynamical simulations, which are beyond the scope
of this paper.  In Figure~\ref{fig:frozen-stream} we show the shape of
a Wilkinoid (gray dotted lines)
